---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab 2 report

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

=======

```{r}
library(classdata)
View(ames)

head(ames)

str(ames)

summary(ames)
```

## Step 1 Results

Inspected the first few lines of the data set. The variables are Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, Total Living Area, Bedrooms, Finished Basement, Lot Area, AC, Fireplace, and Neighborhood. The types of variables are numerical, character, date, and factor/categorical.

**Parcel ID**

-   Character variable that describes ID of sale

**Address**

-   Character variable that states home address

**Style**

-   Factor/Categorical variable that describes the style of the home

-   Has 12 different categories

**Occupancy**

-   Factor/Categorical variable that describes the home occupancy

-   Has 5 different categories

**Sale Date**

-   Date variable of the format "2022-08-12" that records the date of the sale

-   Minimum of 2017-07-03 and maximum of 2022-08-31

**Sale Price**

-   Numerical variable that records the price of the sale

-   Ranges from 0 to 20500000

**Multi Sale**

-   Character variable that indicates whether it was a multi sale or not

**YearBuilt**

-   Numerical variable that records the year the home was built

-   Ranges from 0 (but in reality, 1880) to 2022

**Acres**

-   Numerical variable that records the number of acres the home is

-   Ranges from 0 to 12.012

**TotalLivingArea (sf)**

-   Numerical variable that records the square feet of the living area

-   Ranges from 0 to 6007

**Bedrooms**

-   Numerical variable indicating the number of bedrooms in the home

-   Ranges from 0 to 10

**FinishedBsmtArea (sf)**

-   Numerical variable that states the area of finished basement in square feet

-   Ranges from 10 to 6496

**LotArea (sf)**

-   Numerical variable that states the lot area

-   Ranges from 0 to 523228

**AC**

-   Character variable that indicates if the home has air conditioning or not

**Fireplace**

-   Character variable that indicates if the home has a fireplace or not

**Neighborhood**

-   Factor/categorical variable that state the neighboorhood of the home

-   42 categories

## Step 2 Results

**Sale Price** is the variable that we decided was the variable of interest. There are quite a few *$0* values meaning that they were "sold" for *$0*. We are assuming that meant that there was no sale price for them in the data and instead of *NA* the values assigned was *$0*. 

Other variable of interests include TotalLivingArea and Bedrooms, as they could potentially  be key predictors of price. We focus on uncovering these correlations in Step 4.

## Step 3 Results

The following code creates the histogram for Sale Price. I have log transformed it to show the distribution more accurately.

```{r}
data <- classdata::ames
library(ggplot2)
ggplot(data, aes(x = log(`Sale Price`))) +
  geom_histogram(binwidth = 0.1, fill = "steelblue", color = "black") +
  labs(title = "Histogram of Log(Sale Price)",
       x = "Log(Sale Price)",
       y = "Count") +
  theme_minimal()

```

The following code creates the histogram for Sale Price.

```{r}
ggplot(data, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 10000, fill = "steelblue", color = "black") +
  labs(title = "Histogram of Sale Price",
       x = "Sale Price",
       y = "Count") +
  theme_minimal()
```

The followoing code returns the range of the Sale Price Variable.

```{r}
range_sale_price <- range(data$`Sale Price`, na.rm = TRUE)
range_sale_price
```

Points of interest: There seem to be sale prices of \$0 which does not make sense. It is likely that these 0's represent data that that does not have any value for sale price but is not listed as NA. I believe it is best to remove such observations.

## Step 4 Results

**Grace's Work:** Variable used: TotalLivingArea (sf)

```{r}
summary(ames)
```

The range of TotalLivingArea is 6007 (ranges from 0 to 6007).

```{r}
library(ggplot2)
ggplot(data = ames, mapping = aes(x = `TotalLivingArea (sf)`)) + geom_histogram(binwidth = 10)
ggplot(data = ames, mapping = aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) + geom_point()
ggplot(data = ames, mapping = aes(x = log(`TotalLivingArea (sf)`), y = log(`Sale Price`))) + geom_point()
```

As TotalLivingArea increases, Sale Price also increases, indicating that sale price and total living area have a positive correlation. The two variables do not have a very strong correlation however, as the data points are scattered. There are some outliers; homes with a significantly higher sale price than the others. However, those homes with much higher sale prices don't have a notably high total living area. There are also some homes that have a sale price of $0, which are likely homes that don't have a listed sale price. There are also a couple homes that have a significantly higher total living area than others.

**Akshat's Work**: Variable Used: Bedrooms

The following Code is the code that returns the range of the feature bedroom:

```{r}
range_bedrooms <- range(data$Bedrooms, na.rm = TRUE)
range_bedrooms
```

The following code creates a bar chart of the bedroom variable.

```{r}
ggplot(data, aes(x = Bedrooms)) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(title = "Distribution of Bedrooms",
       x = "Number of Bedrooms",
       y = "Count") +
  theme_minimal()

```

The following code creates a scatterplot of the variables Sale Price and Bedroom. I also went ahead and added a regression line.

```{r}
ggplot(data = data,
       aes(x = `Bedrooms`, y = `Sale Price`)) +
       geom_point() +
       stat_smooth() +
       labs(title = 'Bedrooms vs. Sale Price',
            x = "Number of Bedrooms",
            y = "Sale Price in USD")
```

The discrete variable of bedrooms shows that it is not correlated with Sale Price as there is no obvious pattern that shows that my hypothesis that more bedrooms would be correlated with a higher sale price.

Oddities: There are some houses with a sale price of \$0 as mentioned earlier. We would need to filter the data and remove such observations to have a better understanding of how bedrooms and sale price are correlated.

**Harsh's work**
Variable used: LotArea(sf)

```{r}
library(ggplot2)
ggplot(data = ames, mapping = aes(x = `LotArea(sf)`)) + 
  geom_histogram(binwidth = 5000, fill = "steelblue", color = "black") + 
  labs(title = "Distribution of Lot Area",
       x = "Lot Area",
       y = "Count") + 
  theme_minimal()
ggplot(data = ames, mapping = aes(x = `LotArea(sf)`, y = `Sale Price`)) + 
  geom_point() + 
  labs(title = "Lot Area vs Price",
       x = "Lot Area",
       y = "Price") + 
  theme_minimal()
ggplot(data = ames, mapping = aes(x = log(`LotArea(sf)`), y = log(`Sale Price`))) + 
  geom_point() + 
  labs(title = "log(Lot Area) vs lot(Price)",
       x = "log(Lot Area)",
       y = "lof(price)") + 
  theme_minimal()

```

As Lot Area increases, Sale Price also increases, indicating that sale price and Lot Area have a positive correlation. The two variables do not have a very strong correlation as there are some clusters and a decent spread of the points.

There are some outliers; homes with a significantly higher sale price than the others. Some homes have a much higher sale price and don't have a high Lot Area.
There are some homes that have a sale price of $0, which are most probably homes that don't have a listed sale price.
There are also a few homes that have a significantly higher Lot Area than others, but dont have a much change in sale price.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
